Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-08-20 mice_synthesizing/paper.Rmd
Typo - line break added.
Typo - unordered list.

*Partially synthetic data*
- Explain the idea in more depth than in the intro
- Explain pooling rules by Reiter.
- Adjusted estimate by `synthpop` authors.

@@

Pros and cons of different methods, theoretically and practically.

>>>>

*Partially synthetic data*

- Explain the idea in more depth than in the intro
- Explain pooling rules by Reiter.
- Adjusted estimate by `synthpop` authors.

@@

- Pros and cons of different methods, theoretically and practically.
